partial: An R Package for Creating Partial Dependence Plots

### 2016-08-08 manuscript/greenwell.tex
minor edits
minor updates

PDPs are very useful but can be misleading in the presence of substantial interactions \citep{goldstein-peeking-2015}. To overcome this issue \citeauthor*{goldstein-peeking-2015} developed the concept of \dfn{individual conditional expectation} (ICE) plots -- available in the \CRANpkg{ICEbox} package. \pkg{ICEbox} only allows for one variable at a time (i.e., no multivariate displays), though, color can be used effectively to display information about an additional predictor. The ability to construct derivative plots is also available.

>>>>

PDPs can be misleading in the presence of substantial interactions \citep{goldstein-peeking-2015}. To overcome this issue \citeauthor*{goldstein-peeking-2015} developed the concept of \dfn{individual conditional expectation} (ICE) plots -- available in the \CRANpkg{ICEbox} package. \pkg{ICEbox} only allows for one variable at a time (i.e., no multivariate displays), though color can be used effectively to display information about an additional predictor. The ability to construct derivative plots is also available.
